A new breeding crossover approach for evolutionary algorithms

### 2023-09-22 paper.tex
Late night update.

    We continue with the description for the following set of functions shown in Figure~\ref{fig.experiment_F21-F25}, which includes functions F21 through F25. Results obtained at F21 show that only at 30 dimensions did our proposed strategy prove statistically better. Where at F22 on the 10-dimension, the original OPx was the best, for the 30-dimension, our proposed CRx was declared the winner. On the next F23, the OPx proved better for both tested dimensions. At function F24, on the lower 10-dimension, the CRx was a clear victor, while at the 30-dimension, the original OPx was the most precise. The canonical strategy was the most suitable alternative for the last test operation, F25, only at the 30-dimension.

    We finalize with the description for our last set of functions shown in Figure~\ref{fig.experiment_F26-F30}, which includes functions f26 through F30.

>>>>

    We continue with the description for the following set of functions shown in Figure~\ref{fig.experiment_F21-F25}, which includes functions F21 through F25. Results obtained at F21 show that only at 30 dimensions did our proposed strategy prove statistically better. Where at F22 on the 10-dimension, the original OPx was the best, for the 30-dimension, our proposed CRx was declared the winner. On the next F23, the OPx proved better for both tested dimensions. At function F24, on the lower 10-dimension, the CRx was a clear victor, while at the 30-dimension, the original OPx was the most precise. The canonical strategy was the most suitable alternative for the last test operation, F25, only at the 30-dimension. We finalize with the description for our last set of functions shown in Figure~\ref{fig.experiment_F26-F30}, which includes functions F26 through F30. The statistical test found no clear winner for the crossover alternatives at the mathematical evaluations, F26, F27, and F29. On the other hand, at operation F28, the proposed CRx statistically overcomes the canonical strategy for both tested dimensions. Lastly, at F30, our proposed CRx was the best alternative for the 30-dimension test.
